Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/tex/advanced.tex

  /**
   * @brief Traces confluent state transition
   * A confluent state transition is
   * a simultaneous internal and external transition.
   * @param model The model that just went
   *              through a confluent transition
   */
  void tracesConfluent(const t_atomicmodelptr& adevs,
                       std::size_t coreid);
};
\end{lstlisting}
Even though it is not explicitly enforced, it is highly recommended to derive your custom implementation from the \lstinline{TracerBase} class and to allow the use of output policies.\\
Note that the tracer must not print its output upon generation. To make sure that the output is still generated in the correct order, the tracer must register a \lstinline{TraceMessage}.
\subparagraph{Registering a trace message}
The \lstinline{TraceMessage} class is defined in the \path{src/tracers/tracemessage.h} header file. These messages allow the simulator to schedule output generation and purge unwanted messages upon rollback. They contain the following elements:
\begin{itemize}
	\item[timestamp] The time upon which this message is created. This time can be retrieved either from the model that is being traced or as a separate parameter.
	\item[tracerID] Each tracer should have a unique ID. If multiple tracers are used, this ID makes sure that the tracers cannot interfere with eachother. If your tracer derives from \lstinline{TracerBase}, then this ID is automatically assigned to your tracer. It can be accessed via the \lstinline{getID()} member function.
	\item[execute function] This function is executed when the trace output can be safely sent to an output sink. It is recommended to use \lstinline{std::bind<...>()}. The function must be of type \lstinline{void()}.
	\item[coreID] Each simulation core has an ID. During the simulation, it can happen that some trace messages must be removed based on which core initiated the trace.
	\item[delete function] This function is called when the \lstinline{TraceMessage} is destructed. If the tracer must allocate memory on the heap, this function can be used to free that memory.\\*
		Just like the \emph{execute function}, this function must be of type \lstinline{void()}.
\end{itemize}
When the message is created, it can be scheduled with the free function \lstinline{void scheduleMessage(t_tracemessageptr message)}.\\
Both the \lstinline{TraceMessage} class and the \lstinline{scheduleMessage} function are defined in the \path{src/tracers/tracemessage.h} header. For a more in-depth example, you can always take a look at the implementation of the \lstinline{VerboseTracer} implementation.

>>>>

  /**
   * @brief Traces confluent state transition
   * A confluent state transition is
   * a simultaneous internal and external transition.
   * @param model The model that just went
   *              through a confluent transition
   */
  void tracesConfluent(const t_atomicmodelptr& adevs,
                       std::size_t coreid);
};
\end{lstlisting}
Even though it is not explicitly enforced, it is highly recommended to derive your custom implementation from the \lstinline{TracerBase} class and to allow the use of output policies.\\
Note that the tracer must not print its output upon generation. To make sure that the output is still generated in the correct order, the tracer must register a \lstinline{TraceMessage}.
\subparagraph{Registering a trace message}
The \lstinline{TraceMessage} class is defined in the \path{src/tracers/tracemessage.h} header file. These messages allow the simulator to schedule output generation and purge unwanted messages upon rollback. They contain the following elements:
\begin{itemize}
	\item[timestamp] The time upon which this message is created. This time can be retrieved either from the model that is being traced or as a separate parameter.
	\item[execute function] This function is executed when the trace output can be safely sent to an output sink. It is recommended to use \lstinline{std::bind<...>()}. The function must be of type \lstinline{void()}.
	\item[coreID] Each simulation core has an ID. During the simulation, it can happen that some trace messages must be removed based on which core initiated the trace.
	\item[delete function] This function is called when the \lstinline{TraceMessage} is destructed. If the tracer must allocate memory on the heap, this function can be used to free that memory.\\*
		Just like the \emph{execute function}, this function must be of type \lstinline{void()}.
\end{itemize}
When the message is created, it can be scheduled with the free function \lstinline{void scheduleMessage(t_tracemessageptr message)}.\\
Both the \lstinline{TraceMessage} class and the \lstinline{scheduleMessage} function are defined in the \path{src/tracers/tracemessage.h} header. For a more in-depth example, you can always take a look at the implementation of the \lstinline{VerboseTracer} implementation.
